Roster Review (Generic)

### 2019-07-09 rosterReview_generic.Rmd
All-Star break lineups, some refactoring of views

```{r get_data}
force_fetch <- FALSE
force_join <- FALSE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

if (force_fetch && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
  stop("Need projection files to force a recalc")
} else {
  rosters <- load_players_with_projections(force_fetch, 
                                           force_join, 
                                           batter_file, 
                                           pitcher_file)
}

#TODO review duplicates
```

@@

# TODO get position factor ordering back, consider DL?
rosters_by_position %>% 
  filter(team != "Free Agent",
         type == "pitcher") %>% 
  mutate(position = as.character(position)) %>% 
  droplevels() -> team_pitchers_all

@@

standings_projected <- team_lineups %>% 
  filter(position != 'BN') %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(pos_zar),
            mean_pos_zar = mean(pos_zar),
            median_pos_zar = median(pos_zar),
            var_pos_zar = sd(pos_zar)) %>% 
  arrange(sum_pos_zar %>% desc)

@@

```{r ros_team_rankings}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_adj

@@

team_lineups %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_optimal

@@

standings_projected %>% 
  mutate(sum_pos_zar = sum_pos_zar - median(sum_pos_zar)) %>% 
  mutate(team = fct_reorder(team, sum_pos_zar)) %>% 
  ggplot(aes(team, sum_pos_zar)) +
  geom_col() +
  coord_flip()

#TODO try other graph views, including error bars representing variance
```

```{r free_agents}
#TODO abstract some of these views
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(digits=1)) %>% 
  select(team, name_full, positions, type, zar) %>% 
  View("Available Free Agents")
```

@@

>>>>

```{r get_data}
force_fetch <- TRUE
force_join <- TRUE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

if (force_fetch && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
  stop("Need projection files to force a recalc")
} else {
  rosters <- load_players_with_projections(force_fetch, 
                                           force_join, 
                                           batter_file, 
                                           pitcher_file)
}
```

@@

# TODO consider DL?
# FIXME a few empty position slots for a one or two teams
rosters_by_position %>% 
  filter(team != "Free Agent",
         type == "pitcher") %>% 
  mutate(position = as.character(position)) %>% 
  droplevels() -> team_pitchers_all

@@

standings_projected <- team_lineups %>% 
  filter(position != 'BN') %>% 
  group_by(team) %>% 
  summarize(sum_pos_zar = sum(pos_zar),
            mean_pos_zar = mean(pos_zar),
            median_pos_zar = median(pos_zar),
            var_pos_zar = sd(pos_zar)) %>% 
  mutate(adj_sum_pos_zar = sum_pos_zar - median(sum_pos_zar)) %>% 
  arrange(sum_pos_zar %>% desc)

@@

```{r ros_team_rankings}
rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  mutate(zar = round(zar,2)) %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_adj

@@

team_lineups %>%
  mutate(zar = round(zar,2)) %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_optimal

@@

standings_projected %>% 
  mutate(team = fct_reorder(team, adj_sum_pos_zar)) %>% 
  ggplot(aes(team, adj_sum_pos_zar)) +
  geom_col() +
  geom_errorbar(aes(ymin=adj_sum_pos_zar-var_pos_zar, ymax=adj_sum_pos_zar+var_pos_zar), width = .5) +
  coord_flip()
```

```{r free_agents}
#TODO abstract some of these views
rosters %>% 
  mutate(zar = round(zar)) %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.3) +
  coord_flip() -> pa

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(digits=1)) %>% 
  select(team, name_full, positions, type, zar) %>% 
  View("Available Free Agents")
```

@@

```{r dups}
#FIXME dups 
rosters %>% count(player_id) %>% filter(n > 1) %>% left_join(rosters) -> dups

dups %>% count(team)

dups %>% select(team, manager, name_full, positions)
